Pillar 2 - Topic Modeling

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
app changes

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA
```

@@

@@

#my_LDA
my_LDA <- function(n_topics, corpus){

  LDA_model <- LDA(
    x       = corpus,
    k       = n_topics,
    method  = "Gibbs",
    control = my_control
    )
}

@@

#create folds
create_folds <- function(my_dtm){
  #find number of documents (D)
  D <- nrow(my_dtm)

  #Assign documents to a fold
  folding <- sample(rep(seq_len(10), ceiling(D))[seq_len(D)])
}

#cross-validate
cross_validate <- function(my_dtm){
  #Number of documents (D)
  D <- nrow(my_dtm)

@@

  for(k in n_topics) {
    for(chain in 1:10){
      train_set <- my_dtm[folding != chain, ]
      test_set  <- my_dtm[folding == chain, ]

      training <- my_LDA(k, train_set)
      testing  <- my_LDA(k, train_set)
    }
  }
}

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words, eval = TRUE}
get_top_words <- function(d_beta, n = 3){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
##Convenience vectors for APP
```{r for convenience, eval = T}
# set seed
set.seed(1)

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```

>>>>

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA

library(modelr) #cross_validation
```

@@

```{r}
my_control_fast <- list(

  nstart = 1,
  seed   = 1,
  best   = TRUE,

  burnin = 5,
  iter   = 10,
  thin   = 2

@@

#my_LDA
my_LDA <- function(n_topics, corpus, control = my_control){

  LDA_model <- LDA(
    x       = corpus,
    k       = n_topics,
    method  = "Gibbs",
    control = control
    )
}

@@

this_control <- list(

  nstart = 10,
  seed   = 1 : 10,
  best   = FALSE, #this is different

#
##cross-validate

#crossv_sets returns data.frame with 10-folds divided into train (DTM) and test sets(DTM)
crossv_sets <- function(dtm){
  #Setup
  n_documents <- nrow(dtm)
  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant

  #functions
  create_trainset <- function(Fold){
    train_set = dtm[folding != Fold,]
  }

  create_testset <- function(Fold){
    test_set  = dtm[folding == Fold,]
  }

  #create folds
  folds <-  data.frame(Fold = 1:10) %>%
    mutate(train_set = map(Fold, .f = create_trainset),
           test_set  = map(Fold, .f = create_testset))
  return(folds)
}

cross_validate <- function(my_dtm){
  #Number of documents (D)
  D <- nrow(my_dtm)

@@

  for(k in n_topics) {
    for(chain in 1:10){
      #Sets
      train_set <- my_dtm[folding != chain, ]
      test_set  <- my_dtm[folding == chain, ]

      #LDA
      training      <- LDA(train_set, k = k, control = my_control, method = "Gibbs")

      #best_training <- training@fitted[[which.max(logLik(training))]]
      return(perplexity(training, newdata = test_set))
      #testing  <- my_LDA(test_set, model = best_training, control = list())
    }
  }
}

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words, eval = TRUE}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
####stopwords for keywords
THIS NEEDS CLEANING!!!!!!!!!!!!!!!!!!!!!!!!!
```{r}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

remove_words <- function(x){
  setdiff(x, not_include)
}

kw1 <- lapply(
  kw,
  remove_words
)

```
##Convenience vectors for APP
```{r for convenience, eval = T}
# set seed
set.seed(1)

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
save(kw1, file="App/Recommender System/tmp_data.RDATA")#DELETE LATER
```
